### 2012-06-22 inst/examples/Sethi.Rmd
so far big noise okay

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache.path="Sethi/" or`

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .5
sigma_m <- .5
sigma_i <- .5
````

>>>>

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache.path="Sethi_bignoise/" or`

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .001
sigma_m <- .001
sigma_i <- .5
````
